%-------------------------
% Resume in LaTeX
% Author: Uday Dewasi
% Based off: https://github.com/Udaydewasi/Latex_resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% Uncomment one to use a specific font:
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1in}

\urlstyle{same}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine-readable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{#2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small#2} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \small#2 \\
  \end{tabular*}\vspace{-7pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
% Resume Starts Here
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \textbf{Uday Dewasi}} \\ \vspace{1pt}  
    \href{mailto:udaydewasi2601@gmail.com}{\underline{udaydewasi2601@gmail.com}} $|$
    \href{tel:+917878842019}{\underline{+91-7878842019}} $|$
    \href{https://leetcode.com/Udaydewasi_26}{\underline{leetcode/uday}} $|$
    \href{https://www.linkedin.com/in/uday-dewasi-278aab268/}{\underline{linkedin/uday}} $|$ 
    \href{https://github.com/Udaydewasi}{\underline{github/uday}} $|$
    \href{https://uday-portfolio-two.vercel.app/}{\underline{Portfolio}}
\end{center}

%-----------Education----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
    {MBM University, Jodhpur, Rajasthan}{Sept. 2022 -- May 2026} 
    {B.E. in Computer Science} {SCGPA: 7.61}
\resumeSubheading
    {Govt. Sr. Sec School, Sirohi, Rajasthan}{} 
    {12th | PCM | 82.6\%} {2019 -- 2020}
\resumeSubHeadingListEnd

%-----------Technical Skills----------
\section{Technical Skills}
\textbf{Programming:} C/C++, DSA, OOP, JavaScript (ES6+), Java, SQL, HTML, CSS \\
\textbf{Libraries/Frameworks:} React.js, Node.js, Express.js, PostgreSQL, MongoDB, Tailwind CSS, Redis, WebSocket, API Gateway \\
\textbf{Tools/Platforms:} Git, GitHub, VS Code, Docker, AWS, CI/CD Pipelines \\
\textbf{Operating Systems:} Linux, Windows

%-----------Projects----------

\section*{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{LEARNIFY} $|$ \emph{MongoDB, Node.js, Express.js, React, Tailwind CSS}}{
    \href{https://github.com/Udaydewasi/Learnify}
    {\underline{GitHub Repo.}}}
    \resumeItemListStart
        \resumeItem{Developed a full-fledged MERN stack web application, serving as an EdTech platform, featuring authentication and
role-based access for 3 types of users: students, educators, and administrators.}
        \resumeItem{Utilized React.js for the front-end, Node.js with Express.js for the server-side logic, and MongoDB for efficient data
management.}
        \resumeItem{Features: Authentication, student, admin, and educator profiles, course purchasing, progress tracking, revenue
monitoring, course uploads, and email notifications.}
        \resumeItem{Implemented a secure payment gateway, enabling seamless course purchases and transaction processing.}
    \resumeItemListEnd


\resumeProjectHeading
    {\textbf{WALLET SYSTEM} $|$ \emph{Node.js, React.js, PostgreSQL, MongoDB, Redis, WebSocket, Docker, AWS}} {\href{https://github.com/Udaydewasi/Wallet-System}{\underline{GitHub Repo.}}}
    \resumeItemListStart
        \resumeItem{Designed and deployed a scalable microservices-based wallet system for deposits, transfers, and real-time updates.}
        \resumeItem{Utilized PostgreSQL for wallet management, MongoDB for user authentication, and Redis for caching to improve
performance.}
        \resumeItem{Implemented WebSocket for real-time transaction notifications and centralized routing/security with an API Gateway.}
        \resumeItem{Developed a responsive, user-friendly frontend with React.js and integrated JWT-based authentication for secure
sessions.}
        \resumeItem{Automated deployment using CI/CD pipelines (GitHub Actions), containerized services with Docker, and deployed to
AWS EC2 with images stored in ECR.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------------Experience/Certifications-----------


\section*{Experience/Certifications}

\resumeSubHeadingListStart
    \resumeSubheading
        {Red Hat Certified System Administrator (RHCSA)}{}
        {Certification ID: 240-214-080}  {Issued Date: October 28, 2024}
    \resumeSubheading
    {Volunteering:}{}{}{}
    \vspace{-0.5cm}
    \resumeItemListStart
        \resumeItem{Coordinated a team of 7 members in Encarta university tech fest, managing coding and non-tech competitions.}
        \resumeItem{ Served as department coordinator during the university sports fest, leading cricket and kabaddi teams as captain.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------------Achievements--------------

\section*{Achievements}
\resumeSubHeadingListStart
\resumeSubheading {}{}{}{}
\vspace{-0.9cm}
\resumeItemListStart
    \resumeItem{Winner of Run of Code, The Royal Code, and Coding Chowk competitions in ENCARTA university tech fest.}
    \resumeItem{Solved 900+ challenging DSA coding problems on LeetCode, GFG, and Codeforces.}
    \resumeItem{ESRC workshop: Built a simple and fast line follower robot by using programming language Arduino, Raspberry-pi-
    Pico, motors, and various electronics devices.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}